---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

**NOTE: This small package is a Stat545b project, primarily for the purpose of learning function & package development. 

# timeseries

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

The goal of `timeseries` is to speed up the initial stages of data exploration by providing a quick template for visualizing temporal patterns in data set. 

## Installation

``` r
devtools::install_github("nicolalove/timeseries", build_vignettes = TRUE, ref = "v0.1.0")
```

## Package Development 

As per the specifications of the rubric for Exercise 1.1, I will now explain how I created each part of my R package using the `devtools` and `usethis` packages. 

1. I initialized the package project by loading `library(devtools)` in the RStudio console & used the `create_package` function to create the `timeseries` package. 

2. In a new script under the `timeseries` package R-Project, I manually coded the function `qtseries`, which I developed in *assignment 1-b* of this course. I used the `use_r()` function to save `qtseries` as an .R file in the subdirectory of the `timeseries` package, committed the changes and ran the `load_all()` function to make the `qtseries` function available. Finally, I used the *Check* button under the *Build* tab to ensure that everything was running smoothly so far (I did this several times after each numbered step to ensure that the small changes hadn't caused any errors).

3. I then updated the description file with the relevant information, and specified a license using `use_mit_license()` function. I made sure to update the description file with the dependencies I use in the function, examples and tests using the `use_package()` and `use_pipe()` functions.

4. I used `roxygen2`comment style and tags using `@` to specify the document the `qtseries` function, mostly following along with the recorded first Stat545a lecture on R package development. I looked up some examples for writing functions using `ggplot2` as a dependency, and found that the `ggplot2` developers recommend using the `@importFrom` tag if the new function uses many lines of ggplot functions. This was especially helpful as using the `::` call for every line of ggplot functions was getting messy and made `qtseries` difficult to read. Once I specified all the relevant documentation, I used the `document()` function to save the `roxygen2` inputs. After running another `check()`, I installed the `timeseries` package in my library & restarted my R session via `install()`. 

5. I implemented some formal tests for the `qtseries` function by using `use_testthat()` to add the `testthat` package to the Description file, and used `use_test("qtseries")` to specifically write a test script for `qtseries` function. These tests were developed in *assignment 1-b* of this course, so I just copied and pasted the tests in the *test-qtseries.R* script. I then checked the tests using the `test()` function, as well as using the *Check* button under the *Build* tab to ensure everything was running smoothly. I also ran the `load_all()` function again after this step. 

6. I created a `ReadMe.Rmd` file using the `use_readme_rmd()` function, and added a couple badges using `use_lifecycle_badge("experimental")` and manually writing the link for the MIT license badge. Once I am finished editing this Readme document I will render it using the `build_readme()` function. 

7. I built a vignette with `use_vignette()`, added the relevant information and examples, and then rendered the document using `build_vignette()`. 


## Basic Example

Building a time series plot with a dummy data set

```{r example setup}
testdf <- data.frame(year = rep(seq(from = 1980, to= 1990, 1), 3),
                       rainfall = c(rnorm(11, 100, 30), rnorm(11, 70, 10),rnorm(11, 20, 20)),
                       temp = c(rnorm(11, 70, 30), rnorm(11, 100, 10),rnorm(11, 45, 20)),
                       daysofsun = c(NA, NA, rnorm(9, 280, 50), rnorm(11, 300, 30), NA, rnorm(10, 340, 15)),
                       region = c(rep("A",11), rep("B", 11), rep("C", 11)))
```


```{r example}
library(timeseries)
qtseries(testdf, year, temp, region, verbose = TRUE)
```
